---
output:
  html_document: default
  pdf_document: default
---
## Airbnb Listings Feature Generation
Scraped London listings in Airbnb from Dec 7 2019.
```{r}
library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
```

### Importing csv file
Remember to decompress the gzip file before importing the csv.
```{r}
filepath = "../data/london_dec_19_listings.csv"
raw_data = read.csv(filepath)

firs_review_cutoff = "2019-01-01"
percent_review = 0.5 # percentage of airbnb guests who leave reviews
avg_stay = 5.1 # avg length of stay in city
```

### Selecting columns that might be useful for generating features
```{r}
feature_candidates = c("neighbourhood_cleansed", "price", "last_scraped",
                       "property_type", "room_type", "bathrooms",
                       "bedrooms", "beds", "amenities", "minimum_nights",
                      "maximum_nights", "availability_30", "first_review",
                      "number_of_reviews", "number_of_reviews_ltm",
                      "first_review", "name", "host_identity_verified",
                      "review_scores_accuracy", "review_scores_cleanliness",
                      "review_scores_checkin", "review_scores_communication",
                      "review_scores_location", "review_scores_value",
                      "instant_bookable","reviews_per_month", "latitude",
                      "longitude", "accommodates",
                      "description", "neighborhood_overview",
                      "host_since", "host_about", "host_response_time",
                      "host_response_rate", "host_acceptance_rate",
                      "host_is_superhost", "host_has_profile_pic")
```
Features noted but not in the 2019 dataset: bathrooms_text, number_of_reviews_l30d
Note: Features tend to change between  datasets

```{r}
raw_features = raw_data %>% 
  select(feature_candidates) %>% 
  filter(number_of_reviews_ltm > 0, first_review < firs_review_cutoff)
```

### COnverting prices to numeric values and adding flat_size
flat_size: A grouping where L means large flats (more than 4 guest) and S means small flats for up to 4 guests.
```{r}
#Converting string price to doubles and removing junk
raw_features = raw_features %>% filter(!is.na(price)) %>%
  mutate(num_price = as.numeric(str_replace_all(str_sub(price, 2), ",", ""))) %>%
  filter(num_price > 0) %>% 
  mutate(flat_size = ifelse(accommodates > 4, "L", "S"))
```


### Adding regional price levels 1 - cheapest, 4 - most expensive
```{r}
get_price_level = function(price, p25, p50, p75) {
  return(ifelse(price <= p25, 1,
         ifelse(price <= p50, 2,
         ifelse(price <=p75, 3, 4))))
}

price_groups = raw_features %>% 
  group_by_(.dots=c("neighbourhood_cleansed", "flat_size")) %>%
  summarize(p25 = quantile(num_price, .25), p50 = quantile(num_price, .50), p75 = quantile(num_price, .75))

price_features = left_join(raw_features, price_groups, by = c("neighbourhood_cleansed", "flat_size"))
price_features = price_features %>% mutate(price_level = get_price_level(num_price, p25, p50, p75))
```
### Adding KPI to the dataset
```{r}
get_kpi = function(number_of_reviews, last_scraped, first_review, percent_review, avg_stay) {
  day_delta = round(as.numeric(difftime(last_scraped, first_review, units="days")))
  occupancy_rate = number_of_reviews * avg_stay / day_delta
  return(if_else(occupancy_rate > 1, 1, occupancy_rate))
}

kpi_data = price_features %>% mutate(
  kpi = get_kpi(number_of_reviews, last_scraped, first_review, percent_review, avg_stay))
```

### Use kpi_data dataframe for further improvements (feel free to delete this cell)
```{r}
ggplot(data=kpi_data) +
  geom_histogram(aes(kpi))

head(kpi_data, 5)
```


```{r}
```

```{r}
```

```{r}
```