---
output:
  html_document: 
    fig_width: 10
    fig_height: 7
  pdf_document: default
editor_options: 
  chunk_output_type: inline
---
## Airbnb Listings Feature Generation
Scraped London listings in Airbnb from Dec 7 2019.

```{r}
requirements <- c("ggplot2", "dplyr", "stringr", "tidyr", "ggrepel", "splitstackshape", "devtools")
missing_reqs <- requirements[!(requirements %in% installed.packages()[,"Package"])]

# Uncomment following lines to install additional dependencies:
#devtools::install_github("cardiomoon/ggiraphExtra")
#devtools::install_github("datavisyn/lineup_htmlwidget")
```


```{r}
library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(ggrepel)
library(splitstackshape)
library(ggiraphExtra)
```

### Importing csv file
Remember to decompress the gzip file before importing the csv.
```{r}
filepath = "../data/london_dec_19_listings.csv"
raw_data = read.csv(filepath)

first_review_cutoff = "2019-01-01"
avg_stay = 5.1 # avg length of stay in city
superhost_score = 0.75
```

### Selecting columns that might be useful for generating features
```{r}
feature_candidates = c("neighbourhood_cleansed", "price", "last_scraped",
                       "property_type", "room_type", "bathrooms",
                       "bedrooms", "beds", "amenities", "minimum_nights",
                      "maximum_nights", "availability_30", "first_review",
                      "number_of_reviews", "number_of_reviews_ltm",
                      "first_review", "name", "host_identity_verified",
                      "review_scores_accuracy", "review_scores_cleanliness",
                      "review_scores_checkin", "review_scores_communication",
                      "review_scores_location", "review_scores_value",
                      "instant_bookable","reviews_per_month", "latitude",
                      "longitude", "accommodates",
                      "description", "neighborhood_overview",
                      "host_since", "host_about", "host_response_time",
                      "host_response_rate", "host_acceptance_rate",
                      "host_is_superhost", "host_has_profile_pic")
```
Features noted but not in the 2019 dataset: bathrooms_text, number_of_reviews_l30d
Note: Features tend to change between  datasets

```{r}
raw_features = raw_data %>% 
  select(all_of(feature_candidates)) %>% 
  filter(number_of_reviews_ltm > 0, first_review < first_review_cutoff)
```

### Converting prices to numeric values and adding flat_size
flat_size: A grouping where L means large flats (more than 4 guest) and S means small flats for up to 4 guests.
```{r}
#Converting string price to doubles and removing junk
raw_features = raw_features %>% filter(!is.na(price)) %>%
  mutate(num_price = as.numeric(str_replace_all(str_sub(price, 2), ",", "")) / accommodates) %>%
  filter(num_price > 5)
```

### Adding regional price levels 1 - cheapest, 3 - most expensive
```{r}
get_price_level = function(price, p1, p2) {
  return(ifelse(price <= p1, "1",
         ifelse(price <= p2, "2", "3")))
         
}

price_groups = raw_features %>% 
  group_by(.dots=c("neighbourhood_cleansed")) %>%
  summarize(p1 = quantile(num_price, .80), p2 = quantile(num_price, .97))

price_features = left_join(raw_features, price_groups, by = c("neighbourhood_cleansed"))
price_features = price_features %>% mutate(price_level = get_price_level(num_price, p1, p2))
```

### Adding flat_size and listing type to the dataset
Feel free to adjust these for groupings of your choice
```{r}
price_features = price_features %>%  mutate(
  flat_size = if_else(accommodates > 4, "L", "S"),
  listing_type = if_else(room_type == "Entire home/apt", "house", "room"))
```

### Adding KPIs to the dataset
```{r}
get_kpi = function(number_of_reviews, last_scraped, first_review, avg_stay) {
  day_delta = round(as.numeric(difftime(last_scraped, first_review, units="days")))
  occupancy_rate = number_of_reviews * avg_stay / day_delta
  return(if_else(occupancy_rate > 1, 1, occupancy_rate))
}

kpi_data = price_features %>% mutate(
  kpi = get_kpi(number_of_reviews, last_scraped, first_review, avg_stay))
```

### Adding good and bad perforance to the dataset
```{r}
get_performance_level = function(kpi) {
  return(ifelse(kpi <= quantile(kpi, .25), "low",
         ifelse(kpi <= quantile(kpi, .50), "avg",
         ifelse(kpi <= quantile(kpi, .75), "avg", "high"))))
}
kpi_data = kpi_data %>% mutate(
  kpi_score = get_performance_level(kpi))
```

### Adding amenities
```{r}
trim_amenities = function(amenity) {
  regex = regex("([}{\"])|(translation missing:.*)|[’]|(\\(s\\))")
  a1 = str_replace_all(amenity, regex, "")
  a2 = tolower(str_replace_all(a1, "[/  -]", "_"))
  a3 = str_replace_all(a2, regex(",,"), ",")
  return(trimws(a3, whitespace=","))
}

kpi_data = kpi_data %>% mutate(a = trim_amenities(amenities))
wide_data = cSplit_e(kpi_data, "a", ",", type = "character", fill = 0, drop = F)
```

# Work below:
```{r}
head(wide_data, 5)
```