---
output:
  html_document: 
    fig_width: 10
    fig_height: 7
  pdf_document: default
editor_options: 
  chunk_output_type: inline
---
## Airbnb Listings Feature Generation
Scraped London listings in Airbnb from Dec 7 2019.

```{r}
requirements <- c("ggplot2", "dplyr", "stringr", "tidyr", "ggrepel", "splitstackshape", "devtools", "lineupjs")
missing_reqs <- requirements[!(requirements %in% installed.packages()[,"Package"])]

# Uncomment following lines to install additional dependencies:
#devtools::install_github("cardiomoon/ggiraphExtra")
#devtools::install_github("datavisyn/lineup_htmlwidget")
```


```{r}
library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(ggrepel)
library(splitstackshape)
library(ggiraphExtra)
library(lineupjs)
```

### Importing csv file
Remember to decompress the gzip file before importing the csv.
```{r}
filepath = "../data/london_dec_19_listings.csv"
raw_data = read.csv(filepath)

first_review_cutoff = "2019-01-01"
avg_stay = 5.1 # avg length of stay in city
superhost_score = 0.75
```

### Selecting columns that might be useful for generating features
```{r}
feature_candidates = c("neighbourhood_cleansed", "price", "last_scraped",
                       "property_type", "room_type", "bathrooms",
                       "bedrooms", "beds", "amenities", "minimum_nights",
                      "maximum_nights", "availability_30", "first_review",
                      "number_of_reviews", "number_of_reviews_ltm",
                      "first_review", "name", "host_identity_verified",
                      "review_scores_accuracy", "review_scores_cleanliness",
                      "review_scores_checkin", "review_scores_communication",
                      "review_scores_location", "review_scores_value",
                      "instant_bookable","reviews_per_month", "latitude",
                      "longitude", "accommodates",
                      "description", "neighborhood_overview",
                      "host_since", "host_about", "host_response_time",
                      "host_response_rate", "host_acceptance_rate",
                      "host_is_superhost", "host_has_profile_pic")
```
Features noted but not in the 2019 dataset: bathrooms_text, number_of_reviews_l30d
Note: Features tend to change between  datasets

```{r}
raw_features = raw_data %>% 
  select(all_of(feature_candidates)) %>% 
  filter(number_of_reviews_ltm > 0, as.numeric(first_review) < first_review_cutoff)
```

### Converting prices to numeric values and adding flat_size
flat_size: A grouping where L means large flats (more than 4 guest) and S means small flats for up to 4 guests.
```{r}
#Converting string price to doubles and removing junk
raw_features = raw_features %>% filter(!is.na(price)) %>%
  mutate(num_price = as.numeric(str_replace_all(str_sub(price, 2), ",", "")) / accommodates) %>%
  filter(num_price > 5)
```

### Adding regional price levels 1 - cheapest, 3 - most expensive
```{r}
get_price_level = function(price, p1, p2) {
  return(ifelse(price <= p1, "1",
         ifelse(price <= p2, "2", "3")))
         
}

price_groups = raw_features %>% 
  group_by(.dots=c("neighbourhood_cleansed")) %>%
  summarize(p1 = quantile(num_price, .80), p2 = quantile(num_price, .97))

price_features = left_join(raw_features, price_groups, by = c("neighbourhood_cleansed"))
price_features = price_features %>% mutate(price_level = get_price_level(num_price, p1, p2))
```

### Adding flat_size and listing type to the dataset
Feel free to adjust these for groupings of your choice
```{r}
price_features = price_features %>%  mutate(
  flat_size = if_else(accommodates > 4, "L", "S"),
  listing_type = if_else(room_type == "Entire home/apt", "house", "room"))
```

### Adding KPIs to the dataset
```{r}
get_kpi = function(number_of_reviews, last_scraped, first_review, avg_stay) {
  day_delta = round(as.numeric(difftime(last_scraped, first_review, units="days")))
  occupancy_rate = number_of_reviews * avg_stay / day_delta
  return(if_else(occupancy_rate > 1, 1, occupancy_rate))
}

kpi_data = price_features %>% mutate(
  kpi = get_kpi(number_of_reviews, last_scraped, first_review, avg_stay))
```

### Adding good and bad perforance to the dataset
```{r}
get_performance_level = function(kpi) {
  return(ifelse(kpi <= quantile(kpi, .25), "low",
         ifelse(kpi <= quantile(kpi, .50), "avg",
         ifelse(kpi <= quantile(kpi, .75), "avg", "high"))))
}
kpi_data = kpi_data %>% mutate(
  kpi_score = get_performance_level(kpi))
```

### Adding amenities
```{r}
trim_amenities = function(amenity) {
  regex = regex("([}{\"])|(translation missing:.*)|[’]|(\\(s\\))")
  a1 = str_replace_all(amenity, regex, "")
  a2 = tolower(str_replace_all(a1, "[/  -]", "_"))
  a3 = str_replace_all(a2, regex(",,"), ",")
  return(trimws(a3, whitespace=","))
}

kpi_data = kpi_data %>% mutate(a = trim_amenities(amenities))
wide_data = cSplit_e(kpi_data, "a", ",", type = "character", fill = 0, drop = F)
```

### Distribution of airbnb listing prices across boroughs
Based on the fact that prices in boroughs are skewed to the left we can split them between 3 groups of 0-80% for most flats, 81% - 96% for expensive flats and 97%+ flats for the most expensive outliers.
```{r}
ggplot(wide_data)+
  geom_density(aes(x=num_price), size=1, fill="lightblue", alpha=0.5)+
  scale_x_continuous(limits = c(0, 100), name="Price Per Night")+
  scale_y_continuous(name="Density")+
  facet_wrap(vars(neighbourhood_cleansed))+
  theme(axis.text=element_blank(), axis.ticks=element_blank(),
        panel.grid=element_blank())
```
### Adding amenity scores
```{r}
col_indices = function(cols, data=wide_data) {
  return(which(colnames(data) %in% cols))
}

safety_amnts = c("a_carbon_monoxide_detector", "a_first_aid_kit", "a_lock_on_bedroom_door",
           "a_building_staff", "a_lockbox", "a_safety_card", "a_smoke_detector", "a_fire_extinguisher", "a_fireplace_guards", "a_window_guards", "a_accessible_height_toilet", "a_fixed_grab_bars_for_shower", "a_step_free_shower")

access_amnts = c("a_accessible_height_bed", "a_disabled_parking_spot", "a_fixed_grab_bars_for_toilet", "a_no_stairs_or_steps_to_enter", "a_wheelchair_accessible", "a_building_staff", "a_ground_floor_access")

comfort_amnts = c("a_essentials", "a_air_conditioning", "a_balcony", "a_bidet", "a_buzzer_wireless_intercom", "a_ceiling_fan", "a_central_air_conditioning", "a_dryer", "a_heat_lamps", "a_iron", "a_jetted_tub", "a_long_term_stays_allowed", "a_memory_foam_mattress", "a_rain_shower", "a_room_darkening_shades", "a_24_hour_check_in", "a_air_purifier", "a_extra_space_around_bed", "a_heated_floors", "a_hot_tub", "a_luggage_dropoff_allowed", "a_patio_or_balcony", "a_terrace")

children_amnts = c("a_baby_bath", "a_babysitter_recommendations", "a_childrens_books_and_toys", "a_crib", "a_family_kid_friendly", "a_baby_monitor")

cooking_amnts = c("a_bread_maker", "a_bbq_grill","a_convection_oven", "a_dishwasher", "a_gas_oven", "a_kitchen", "a_mini_fridge", "a_steam_oven", "a_stove", "a_breakfast", "a_coffee_maker", "a_cooking_basics", "a_dishes_and_silverware", "a_espresso_machine", "a_full_kitchen", "a_microwave", "a_oven", "a_wine_cooler")

work_amnts = c("a_printer", "a_ethernet_connection", "a_fax_machine", "a_high_resolution_computer_monitor", "a_internet", "a_wifi")

leisure_amnts = c("a_bbq_grill", "a_game_console", "a_gym", "a_hammock", "a_indoor_fireplace", "a_pool", "a_sauna", "a_shared_pool", "a_smart_tv", "a_sound_system", "a_tennis_court", "a_amazon_echo", "a_cable_tv", "a_dvd_player", "a_exercise_equipment", "a_fire_pit", "a_garden_or_backyard", "a_hbo_go", "a_internet", "a_netflix", "a_projector_and_screen", "a_shared_gym",  "a_suitable_for_events", "a_tv", "a_wifi")

safety_cols = col_indices(safety_amnts)
access_cols = col_indices(access_amnts)
comfort_cols = col_indices(comfort_amnts)
children_cols = col_indices(children_amnts)
cooking_cols = col_indices(cooking_amnts)
work_cols = col_indices(work_amnts)
leisure_cols = col_indices(leisure_amnts)

wide_data = wide_data %>% mutate(safety = rowSums(.[safety_cols])/length(safety_amnts),
                     access = rowSums(.[access_cols])/length(access_amnts),
                     comfort = rowSums(.[comfort_cols])/length(comfort_amnts),
                     children = rowSums(.[children_cols])/length(children_amnts),
                     cooking = rowSums(.[cooking_cols])/length(cooking_amnts),
                     work = rowSums(.[work_cols])/length(work_amnts),
                     leisure = rowSums(.[leisure_cols])/length(leisure_amnts))
```


```{r}
wide_data = wide_data %>% mutate(listing_type = if_else(room_type == "Entire home/apt", "house", "room"))

radar2 = wide_data %>% filter(kpi_score %in% c("low","high")) %>% select(listing_type, kpi_score, safety, access, comfort, children, cooking, work, leisure)
radar_plot = ggRadar(data=radar2, alpha=0.05, mapping=aes(facet=listing_type, color=kpi_score), size=3)+
  theme(legend.position="bottom", axis.ticks=element_blank(),
        axis.text.y=element_blank(), panel.background = element_rect(color="black", fill="white"),
        panel.grid = element_line(linetype = 2, color="grey"), axis.text.x=element_text(face="bold", size=12))
              
radar_plot
```

# Getting relevant review columns
```{r}
review_cols = c("price_level","kpi_score","review_scores_cleanliness",
                      "review_scores_location", "review_scores_value"
                      )

review_data = wide_data %>% 
  select(all_of(review_cols)) %>% 
  filter(kpi_score != "avg")

review_data <- review_data %>% group_by(price_level, kpi_score) %>% 
  summarise(
    cleanliness = mean(na.omit(review_scores_cleanliness)),
    location = mean(na.omit(review_scores_location)),
    value = mean(na.omit(review_scores_value))
  )
```

# Reviews Lineup
```{r}
lineup(review_data)
```
