---
output:
  html_document: default
  pdf_document: default
---
## Airbnb Listings Feature Generation
Scraped London listings in Airbnb from Dec 7 2019.

```{r}
requirements <- c("ggplot2", "dplyr", "stringr", "tidyr", "ggrepel", "splitstackshape", "stringr","RColorBrewer","OIdata","plotly")
missing_reqs <- requirements[!(requirements %in% installed.packages()[,"Package"])]
if(length(missing_reqs)) install.packages(missing_reqs)
```


```{r}
library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(ggrepel)
library(splitstackshape)
library(stringr)
library(RColorBrewer)
library(OIdata)
library(plotly)
```

### Importing csv file
Remember to decompress the gzip file before importing the csv.
```{r}
filepath = "../data/london_dec_19_listings.csv"
raw_data = read.csv(filepath)

first_review_cutoff = "2019-01-01"
avg_stay = 5.1 # avg length of stay in city
superhost_score = 0.75
```

### Selecting columns that might be useful for generating features
```{r}
feature_candidates = c("neighbourhood_cleansed", "price", "last_scraped",
                       "property_type", "room_type", "bathrooms",
                       "bedrooms", "beds", "amenities", "minimum_nights",
                      "maximum_nights", "availability_30", "first_review",
                      "number_of_reviews", "number_of_reviews_ltm",
                      "first_review", "name", "host_identity_verified",
                      "review_scores_accuracy", "review_scores_cleanliness",
                      "review_scores_checkin", "review_scores_communication",
                      "review_scores_location", "review_scores_value",
                      "instant_bookable","reviews_per_month", "latitude",
                      "longitude", "accommodates",
                      "description", "neighborhood_overview",
                      "host_since", "host_about", "host_response_time",
                      "host_response_rate", "host_acceptance_rate",
                      "host_is_superhost", "host_has_profile_pic")
```
Features noted but not in the 2019 dataset: bathrooms_text, number_of_reviews_l30d
Note: Features tend to change between  datasets

```{r}
raw_features = raw_data %>% 
  select(all_of(feature_candidates)) %>% 
  filter(number_of_reviews_ltm > 0, first_review < first_review_cutoff)
```

### Converting prices to numeric values and adding flat_size
flat_size: A grouping where L means large flats (more than 4 guest) and S means small flats for up to 4 guests.
```{r}
#Converting string price to doubles and removing junk
raw_features = raw_features %>% filter(!is.na(price)) %>%
  mutate(num_price = as.numeric(str_replace_all(str_sub(price, 2), ",", ""))) %>%
  filter(num_price > 0) %>% 
  mutate(flat_size = ifelse(accommodates > 4, "L", "S"))
```

### Adding regional price levels 1 - cheapest, 4 - most expensive
```{r}
get_price_level = function(price, p25, p50, p75) {
  return(ifelse(price <= p25, "1",
         ifelse(price <= p50, "2",
         ifelse(price <=p75, "3", "4"))))
}

price_groups = raw_features %>% 
  group_by_(.dots=c("neighbourhood_cleansed", "flat_size")) %>%
  summarize(p25 = quantile(num_price, .25), p50 = quantile(num_price, .50), p75 = quantile(num_price, .75))

price_features = left_join(raw_features, price_groups, by = c("neighbourhood_cleansed", "flat_size"))
price_features = price_features %>% mutate(price_level = get_price_level(num_price, p25, p50, p75))
```

### Adding KPIs to the dataset
```{r}
get_kpi = function(number_of_reviews, last_scraped, first_review, avg_stay) {
  day_delta = round(as.numeric(difftime(last_scraped, first_review, units="days")))
  occupancy_rate = number_of_reviews * avg_stay / day_delta
  return(if_else(occupancy_rate > 1, 1, occupancy_rate))
}

kpi_data = price_features %>% mutate(
  kpi = get_kpi(number_of_reviews, last_scraped, first_review, avg_stay))
```

### Adding good and bad perforance to the dataset
```{r}
get_performance_level = function(kpi) {
  return(ifelse(kpi <= quantile(kpi, .25), "low",
         ifelse(kpi <= quantile(kpi, .50), NaN,
         ifelse(kpi <= quantile(kpi, .75), NaN, "high"))))
}
kpi_data = kpi_data %>% mutate(
  kpi_score = get_performance_level(kpi))
```

### Adding amenities
```{r}
trim_amenities = function(amenity) {
  regex = regex("([}{\"])|(translation missing:.*)|[’]|(\\(s\\))")
  a1 = str_replace_all(amenity, regex, "")
  a2 = tolower(str_replace_all(a1, "[/  -]", "_"))
  a3 = str_replace_all(a2, regex(",,"), ",")
  return(trimws(a3, whitespace=","))
}

kpi_data = kpi_data %>% mutate(a = trim_amenities(amenities))
wide_data = cSplit_e(kpi_data, "a", ",", type = "character", fill = 0, drop = F)
```


### Looking at postings information
In this part, we will be looking at the impact on the performance of words in the description of Airbnb's listings per neighbourhood. We will also factor in the number of listings per neighbourhood so that we can see the importance of each word.
For that we grouped the descriptions per neighbourhood and per kpi score of low or high. Then we split these descriptions per word to be able to count their frequency. 
The end dataframe has the highest frequency word per neighbourhood for low and for high performance.
```{r}
## I chose to perform the analysis on the description, as it is a main part of the listing, but the following analysis could also have been done for the summary, the name, the neighborhood_overview, the notes and the house rules.

#this function concatenates texts
p <- function(v) {
  Reduce(f=paste, x = v)
}
#selecting a subset of the dataframe to work with. I am using the column chosen by the function, the neighbourhoods and the kpi score (only low and high, not the average), which is all I need for this analysis 
description_analysis=kpi_data %>%
  select(neighbourhood_cleansed, description,kpi_score) %>%
  filter(kpi_score=="low"| kpi_score=="high")

#putting all the text to lower case to be able to compare words
description_analysis$description_cleansed=str_to_lower(description_analysis$description)

#grouping the strings by neighbourhood and kpi score
description_analysis=description_analysis %>%
  group_by(neighbourhood_cleansed,kpi_score) %>%
  summarise(descrip = p(description_cleansed), nbr_listings=n()) 

#splitting the text by word
description_analysis$descrip=str_split(description_analysis$descrip, boundary("word"))

#list of words that do not give any insights and are frequent and should be not taken into account
ignore_words=c("the","a","is","to","and","with","in","of","for","from","are","will","our","you","your","it","by","be","we","on","very","or","has","have","this","at","can","room","an","its","london","there","flat","house","apartment","bedroom","kitchen","all","bed","double","as","i","bathroom","2","area","large","living","home","street","station","away","close","my","also","guests","one","located","access","minute","if","provide","which","minutes")

description_best <- data.frame(matrix(ncol = 4, nrow = 33))
colnames(description_best) <- c('neighbourhood', 'high_kpi_descript', 'low_kpi_descript','nbr_listings')
j=1
for (i in 1:nrow(description_analysis)){
  #taking out basic words that do not give any insights
  description_analysis$descrip[[i]]=description_analysis$descrip[[i]][!description_analysis$descrip[[i]] %in% ignore_words]
  #selecting the most frequent word for high and low kpi per neighbourhood
  #as the data is organised first by kpi=high and then kpi=low, this if/else structure allows to regroup easily on one row the 2
  if(description_analysis$kpi_score[[i]]=="high"){
    description_best$neighbourhood[j]=description_analysis$neighbourhood_cleansed[[i]]
    description_best$high_kpi_descript[j]=as.character(as.data.frame(sort(table(description_analysis$descrip[[i]]),decreasing = TRUE))[1,1])
    description_best$nbr_listings[j]=description_analysis$nbr_listings[[i]]
  }
  else{
    description_best$low_kpi_descript[j]=as.character(as.data.frame(sort(table(description_analysis$descrip[[i]]),decreasing = TRUE))[1,1])
    description_best$nbr_listings[j]=description_best$nbr_listings[j]+description_analysis$nbr_listings[[i]]
    j=j+1
  }
}

```

Then, after loading the coordinates of the London's boroughs and making a few adjustments to the neighbourhoods' name so that we can merge this dataset with my dataset, we calculate the mean longitude and latitude so that we have a point for each neighbourhood to place the word on the map.
Then we plot the two maps, with the words per neighbourhood in each neighbourhood and the color gradient for the number of listings in each neighbourhood.

```{r}
#replacing & for "and" and deleting " upon Thames" from the neighbourhood to be able to merge my dataset and the map
data(london_boroughs)
LB=london_boroughs
LB$name=gsub( "&", "and",LB$name)  #to make them match with our dataset
description_best$neighbourhood=gsub(" upon Thames","",description_best$neighbourhood) 
# merge datasets together
text_map <- LB %>% 
  left_join(description_best, by = c("name"="neighbourhood"))
text_map=na.omit(text_map) #delete rows with NA is resulting join

#get the mean of longitude and latitude to put the selected word in that position.
summary=text_map %>% 
  group_by(name) %>% 
  summarise(mean_long = mean(x),
            mean_lat = mean(y),
            low_kpi_descript = first(low_kpi_descript),
            high_kpi_descript = first(high_kpi_descript),
            nbr_listings=first(nbr_listings))

#for those 4 cases, moving the text a bit so that everything is visible in the end map
summary[summary['name']=='Hammersmith and Fulham','mean_lat']=summary[summary['name']=='Hammersmith and Fulham','mean_lat']-1000
summary[summary['name']=='Wandsworth','mean_long']=summary[summary['name']=='Wandsworth','mean_long']-1000
summary[summary['name']=='Hackney','mean_lat']=summary[summary['name']=='Hackney','mean_lat']-1000
summary[summary['name']=='Islington','mean_lat']=summary[summary['name']=='Islington','mean_lat']+1500

# Plotting london map for high kpi
ggplot()+geom_polygon(data=text_map, aes(x=x, y=y, group = name, fill=nbr_listings),colour="grey") +
  geom_text(data=summary,aes(x=mean_long, y=mean_lat, label = high_kpi_descript), size=3.5, fontface="bold")+
  scale_fill_gradient(low = 'white', high = 'dodgerblue') + 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
          axis.text.y=element_blank(),axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          plot.title = element_text(face="bold"),
          panel.background=element_blank(),panel.border=element_blank(),panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),plot.background=element_blank())+
    labs(title = "Most frequent word in listing's description by London Boroughs",
                subtitle = "For high performing AirBnBs")
#ggsave('london_boroughs_high.png')

# Plotting london map for low kpi
ggplot()+geom_polygon(data=text_map, aes(x=x, y=y, group = name, fill=nbr_listings),colour="grey") +
  geom_text(data=summary,aes(x=mean_long, y=mean_lat, label = low_kpi_descript), size=3.5, fontface="bold")+
  scale_fill_gradient(low = 'white', high = 'dodgerblue') +
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
          axis.text.y=element_blank(),axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          plot.title = element_text(face="bold"),
          panel.background=element_blank(),panel.border=element_blank(),panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),plot.background=element_blank())+
    labs(title = "Most frequent word in listing's description by London Boroughs",
                subtitle = "For low performing AirBnBs")

#ggsave('london_boroughs_low.png')
```


```{r}
# I will create a function so that the text map can be produced for different column with string data.
col_name='neighborhood_overview'
data(london_boroughs)
LB=london_boroughs
#getting the london boroughs map

p <- function(v) {
  Reduce(f=paste, x = v)
}

#selecting and grouping the data :
data_select<-function(col_name,kpi_data) {
  #selecting a subset of the dataframe to work with. I am using the column chosen by the function, the neighbourhoods and the kpi score (only low and high, not the average), which is all I need for this analysis 
  col_analysis=kpi_data %>%
    select(neighbourhood_cleansed, col_name ,kpi_score) %>%
    filter(kpi_score=="low"| kpi_score=="high")
  
  #putting all the text to lower case to be able to compare words
  col_analysis$col_cleansed=str_to_lower(col_analysis[col_name])
  
  #grouping the strings by neighbourhood and kpi score
  col_analysis=col_analysis %>%
    group_by(neighbourhood_cleansed,kpi_score) %>%
    summarise(col = p(col_cleansed), nbr_listings=n()) 
  
  #splitting the text by word
  col_analysis$col=str_split(col_analysis$col, boundary("word"))
  
  col_best <- data.frame(matrix(ncol = 4, nrow = 33))
  colnames(col_best) <- c('neighbourhood', 'high_kpi', 'low_kpi','nbr_listings')
  j=1
  for (i in 1:nrow(col_analysis)){
    #taking out basic words that do not give any insights
    col_analysis$col[[i]]=col_analysis$col[[i]][!col_analysis$col[[i]] %in% c("the","a","is","to","and","with","in","of","for","from","are","will","our","you","your","it","by","be","we","on","very","or","has","have","this","at","can","room","an","its","london","there","flat","house","apartment","bedroom","kitchen","all","bed","double","as","i","bathroom","2","area","large","living","home","street","station","away","close","my","also","guests","one","located","access","minute","if","provide","which","minutes")]
    #selecting the most frequent word for high and low kpi per neighbourhood
    # as the data is organised first by kpi=high and then kpi=low, this if/else structure allows to regroup easily on one row the 2
    if(col_analysis$kpi_score[[i]]=="high"){
      col_best$neighbourhood[j]=col_analysis$neighbourhood_cleansed[[i]]
      col_best$high_kpi[j]=as.character(as.data.frame(sort(table(col_analysis$col[[i]]),decreasing = TRUE))[1,1])
      col_best$nbr_listings[j]=col_analysis$nbr_listings[[i]]
    }
    else{
      col_best$low_kpi[j]=as.character(as.data.frame(sort(table(col_analysis$col[[i]]),decreasing = TRUE))[1,1])
      col_best$nbr_listings[j]=col_best$nbr_listings[j]+col_analysis$nbr_listings[[i]]
      j=j+1
    }
  }
  return (col_best)
}

#merging the london boroughs maps with col_best
prepare_maps_data<-function(LB,col_best){
  #replacing & for "and" and deleting " upon Thames" from the neighbourhood to be able to merge my dataset and the map
  LB$name=gsub( "&", "and",LB$name)  #to make them match with our dataset
  col_best$neighbourhood=gsub(" upon Thames","",col_best$neighbourhood) 
  
  # merge datasets together
  text_map <- LB %>% 
    left_join(col_best, by = c("name"="neighbourhood"))
  text_map=na.omit(text_map) #delete rows with NA is resulting join
  
  #get the mean of longitude and latitude to put the selected word in that position.
  summary=text_map %>% 
    group_by(name) %>% 
    summarise(mean_long = mean(x),
              mean_lat = mean(y),
              low_kpi = first(low_kpi),
              high_kpit = first(high_kpi),
              nbr_listings=first(nbr_listings))
  
  
  #for those 4 cases, moving the text a bit so that everything is visible in the end map
  summary[summary['name']=='Hammersmith and Fulham','mean_lat']=summary[summary['name']=='Hammersmith and Fulham','mean_lat']-1000
  summary[summary['name']=='Wandsworth','mean_long']=summary[summary['name']=='Wandsworth','mean_long']-1000
  summary[summary['name']=='Hackney','mean_lat']=summary[summary['name']=='Hackney','mean_lat']-1000
  summary[summary['name']=='Islington','mean_lat']=summary[summary['name']=='Islington','mean_lat']+1500
  return (summary)
}

text_map<-function(col_name,kpi_data){
  col_best=data_select(col_name,kpi_data)
  summary=prepare_maps_data(LB,col_best)
  
  # Plotting london map for high kpi
  ggplot()+geom_polygon(data=text_map, aes(x=x, y=y, group = name, fill=nbr_listings),colour="grey") +
    geom_text(data=summary,aes(x=mean_long, y=mean_lat, label = high_kpi), size=3.5, fontface="bold")+
    scale_fill_gradient(low = 'white', high = 'dodgerblue') + 
    theme(axis.line=element_blank(),axis.text.x=element_blank(),
            axis.text.y=element_blank(),axis.ticks=element_blank(),
            axis.title.x=element_blank(),
            axis.title.y=element_blank(),
            plot.title = element_text(face="bold"),
            panel.background=element_blank(),panel.border=element_blank(),panel.grid.major=element_blank(),
            panel.grid.minor=element_blank(),plot.background=element_blank())+
      labs(title = "Most frequent word in listing's description by London Boroughs",
                  subtitle = "For high performing Airbnbs")
  
  # Plotting london map for low kpi
  ggplot()+geom_polygon(data=text_map, aes(x=x, y=y, group = name, fill=nbr_listings),colour="grey") +
    geom_text(data=summary,aes(x=mean_long, y=mean_lat, label = low_kpi), size=3.5, fontface="bold")+
    scale_fill_gradient(low = 'white', high = 'dodgerblue') +
    theme(axis.line=element_blank(),axis.text.x=element_blank(),
            axis.text.y=element_blank(),axis.ticks=element_blank(),
            axis.title.x=element_blank(),
            axis.title.y=element_blank(),
            plot.title = element_text(face="bold"),
            panel.background=element_blank(),panel.border=element_blank(),panel.grid.major=element_blank(),
            panel.grid.minor=element_blank(),plot.background=element_blank())+
      labs(title = "Most frequent word in listing's description by London Boroughs",
                  subtitle = "For low performing Airbnbs")

}
```
